Data Visualisation in R

### 2024-11-03 inst/tutorials/MSc_Data_Vis/MSc_Data_Vis.Rmd
Fixed an Ex 6 bug

---
title: "Data Visualisation in R"
author: Dr Susan Johnston [Susan.Johnston@ed.ac.uk](mailto:Susan.Johnston@ed.ac.uk)
date: "1st November 2023"
output: learnr::tutorial
runtime: shiny_prerendered
description: Practical session on data visualisation with ggplot2. Demonstrator - Sarah Dobson.
---

@@

@@

>>>>

---
title: "Data Visualisation in R"
author: Dr Susan Johnston [Susan.Johnston@ed.ac.uk](mailto:Susan.Johnston@ed.ac.uk)
date: "6th November 2024"
output: learnr::tutorial
runtime: shiny_prerendered
description: Practical session on data visualisation with ggplot2.
---

@@

```{r Ex6, exercise = T}

@@

ggplot(penguins, aes(x = species, y = flipper_length_mm)) +
  geom_boxplot() +

  geom_jitter(width = 0.3, alpha = 0.3) +
  theme_bw() +
  labs(x = "Species", y = "Flipper Length (mm)", col = "Species") +
  theme(axis.text.x = element_text(angle = 270, vjust = 0.2, hjust = 0),
        axis.title = element_text(size = 16),
        panel.background = element_rect(fill = "lightblue"))
